### 2018-09-20 Paper_HTML/Paper_HTML.Rmd

# opts_knit$set(root.dir = "C:/Users/rafal/Google Drive/LAMFO/AutomationJobs")
opts_knit$set(root.dir = "C:/Users/B2657804/Google Drive/LAMFO/AutomationJobs")

@@

p <- plot_ly(g, x=~year, y=~`1`, name = "Job Zone 1", marker=list(color=mycolors[1]), 
             line=list(color=mycolors[1]),type = 'scatter', mode = 'lines+markers') %>% 
  add_trace(y = ~`2`, name = "Job Zone 2", marker=list(color=mycolors[2]), line=list(color=mycolors[2])) %>% 
  add_trace(y = ~`3`, name = "Job Zone 3", marker=list(color=mycolors[3]), line=list(color=mycolors[3])) %>% 
  add_trace(y = ~`4`, name = "Job Zone 4", marker=list(color=mycolors[4]), line=list(color=mycolors[4]))%>% 
  add_trace(y = ~`5`, name = "Job Zone 5", marker=list(color=mycolors[5]), line=list(color=mycolors[5]))%>% 
  add_trace(y = ~GDP, name = "PIB Acumulado", marker=list(color =mycolors[6]), line = list(color =mycolors[6])) %>%
  layout( legend = list(orientation = 'h'), xaxis = list(title = " "),
          yaxis = list(title = "Taxa de Crescimento Acumulado"), hovermode = "compare")
p

```

@@

```{r save}
saveRDS(ggplotly(a), "Box_Paper.RDS")
saveRDS(p, "Serie_Paper.RDS")
```

>>>>

opts_knit$set(root.dir = "C:/Users/rafal/Google Drive/LAMFO/AutomationJobs")
# opts_knit$set(root.dir = "C:/Users/B2657804/Google Drive/LAMFO/AutomationJobs")

@@

p <- plot_ly(g, x=~year, y=~`1`, name = "Job Zone 1", marker=list(color=mycolors[1]), 
             line=list(color=mycolors[1]),type = 'scatter', mode = 'lines+markers') %>% 
  add_trace(y = ~`2`, name = "Job Zone 2", marker=list(color=mycolors[2]), line=list(color=mycolors[2])) %>% 
  add_trace(y = ~`3`, name = "Job Zone 3", marker=list(color=mycolors[3]), line=list(color=mycolors[3])) %>% 
  add_trace(y = ~`4`, name = "Job Zone 4", marker=list(color=mycolors[4]), line=list(color=mycolors[4]))%>% 
  add_trace(y = ~`5`, name = "Job Zone 5", marker=list(color=mycolors[5]), line=list(color=mycolors[5]))%>% 
  add_trace(y = ~GDP, name = "PIB Acumulado", marker=list(color =mycolors[6]), line = list(color =mycolors[6])) %>%
  layout( legend = list(orientation = 'h'), xaxis = list(title = " "),
          yaxis = list(title = "Taxa de Crescimento Acumulado"), hovermode = "compare")
p
```

@@

```{r save}
saveRDS(a, "Box_Paper.RDS")
saveRDS(g, "Serie_Paper.RDS")
```
